Cryptographic assurance of secrecy and fairness in voting

### 2012-12-07 paper/paper.tex
pv

It is important that we have considered secrecy mechanisms first, as these strategies enable
fulfillment of other goals, such as \emph{verifiability}.

@@

The same can be said for \term{Helios}, should it be implemented with inappropriate primitives (not ElGamal
and SHA-1); however, as the authors have designed the scheme with particular primitives in mind, its
specification is less open to interpretation and, therefore, potentially harmful choices.

>>>>

@@

The same can be said for \term{\pv{}} and \term{Helios}, should they be implemented with inappropriate primitives; however, as the authors have designed the schemes with particular primitives in mind, their
specifications are less open to interpretation and, therefore, potentially harmful choices.
